Approximation Algorithms: Greedy Algorithm and Local Search

### 2024-05-02 paper/paper.tex
optimized with grammarly

\title{Approximation Algorithms: Greedy Algorithm and Local Search}
\author{Zixuan Fan\thanks{Department of Computer Science, Technical University of Munich. {\tt ge43yeb@mytum.de}}}
\maketitle

\section{Introduction}
The theory of computer science has grown significant throughout the past century. Among many topics, \NP-hardness has drawn the attention of many researchers. 
While there is no proof whether $\PTIME=\NP$, people tend to be interested in compensation: solving NP-hard problems with a sub-optimal solution in polynomial time.
This is the motivation of approximation algorithms. This paper introduces two fundamental techniques in designing approximation algorithms: greedy algorithm and local search.
We start with some mathematical backgrounds, followed by a brief introduction of greedy and local search. 
Then, we present a few examples that exploit these techniques.

@@

\subsection{Greedy Algorithms and Local Search}
Both greedy algorithms and local search contructs the solution step by step. 
In each step, the strategy makes certain desicions such that the result is locally optimal. 
The difference between two techniques lies in the strategy of making decisions. 
The greedy algorithms try to make the best decision at each step, the solution is not guaranted to 
be \textit{feasible} at the beginning. On the other hand, local search starts with an arbitrary feasible solution,
and maintains the feasibility while improving the solution. 
Hence greedy algorithms are called \textit{primal infeasible} algorithms, while local search algorithms 
are referred to as \textit{primal feasible} algorithms.

\section{Scheduling on A Single Machine}
Scheduling or Job Sequencing, is one of the earliest discovered NP-complete problems. 
It was amongst the first 21 NP-complete problems published by Karp in 1972. In this section, 
we examine a simplified version of the problem: only one machine is available for scheduling.
\begin{definition}[Scheduling on Single Machine]
    Given $n$ jobs to be processed with processing time $p_j$, release time $r_j \geq 0$, and deadline $d_j$ with $j = 1, \cdots, n$.
    Suppose $j$-th job is completed at time $C_j$, we define the lateness as $L_j = C_j - d_j$. The goal is minimizing the maximal lateness 
    \begin{align*}
        L_{max} = \max_{j = 1, \cdots, n} L_j
    \end{align*}
\end{definition} 
Unfortunately, the problem is \NP-hard, and it remains \NP-hard even if we apply 
a few constraints to it. \textbf{cite the source} One exceptional case is when all deadlines are non-negative: the lateness is always positive. 
We are able to give a 2-approximation algorithm for this case. The algorithm simply exploits the earliest due date rule(\textbf{EDD}). 
Just as the name suggests, whenever the machine finishes a job, it picks the job with the earliest due date from all \textbf{available} jobs.
Here, a job is \textit{available} at time $t$ if $r_j \leq t$.

To analyze the algorithm, we have to introduce a few notations. Let $S$ denote a set of jobs, $r(S) = \min_{j \in S} r_j$, $p(S) = \sum_{j \in S} p_j$, 
and $d(S) = \max_{j \in S} d_j$. While $L_{max}$ denotes the maximal lateness computed by the algorithm, $L_{max}^*$ denotes the optimal solution. 
As preparation, an interesting lowerbound on the optimal solution is observed. 
\begin{lemma}
    \label{lemma:lowerbound}
    For any set of jobs $S$, $L_{max}^* \geq r(S) + p(S) - d(S)$
\end{lemma}
\begin{proof}
    Suppose job $j$ is the last finished job in the optimal schedule. The scheduling cannot start until $r(S)$. In an optimal schedule, there is no gap between the processing of jobs, all jobs 
    are processed consecutively in $p(S)$. Hence $j$ cannot be finished until $r(S) + p(S)$. In addition, we have $d_j \leq d(S)$ by definition. It follows 
    \begin{align*}
        L_{max}^* \geq L_j = C_j - d_j \geq r(S) + p(S) - d_j \geq r(S) + p(S) - d(S)
    \end{align*} 
\end{proof}
We then take a closer look at the \textbf{EDD} rule. Suppose the release time $r_j$, processing time $p_j$, and the deadline $d_j$ are encoded as a ternary tuple $(r_j, p_j, d_j)$.
The only part the requires heavy computation for \textbf{EDD} rule is choosing the job with the earliest due date.
The easiest implementation is preserve a linked list to store the information of each job, which takes $\bigo{n^2}$ time in total. 
A more efficient implementation takes advantage of a FIFO queue, which takes only $\bigo{n}$ time. In either cases, 
the algorithm runs in polynomial time. This directly leads to the following theorem.
\begin{theorem}
    The EDD-rule algorithm runs in polynomial time. 
\end{theorem}
What we care more in the context of approximation algorithms is the approximation ratio. We then show that the algorithm yields the promised approximation ratio.
\begin{theorem}
    The EDD-rule algorithm yields a 2-approximation ratio.
\end{theorem}
\begin{proof}
    Suppose $j$ is the job with the maximal lateness in the schedule generated by the \textbf{EDD} rule.
    Let $t$ be the earliest time such that the machine keeps processing jobs continuously in the interval $[t, C_j]$.
    Let $S$ be the set of jobs that are processed in this interval. In our assumption, $r(S) = t$ is guaranteed. 
    Suppose for contradiction that $r(S) > t$, the processing would not be able to start at time $t$. 
    Similarly, if $r(S) < t$, the processing would start earlier than $t$. Both cases contradict the assumption.
    Furthermore, $p(S) = C_j - t$, for the processing is continuous and it stops at time $C_j$. Applying lemma \cref{lemma:lowerbound},
    we obtain 
    \begin{align*}
        L_{max}^* \geq r(S) + p(S) - d(S) = t + C_j - t - d(S) = C_j - d(S) \geq C_j
    \end{align*}
    Additionally, it holds $d_j < d(S)$ by definition. Applying the same lemma, we have
    \begin{align*}
        L_{max}^* \geq r(S) + p(S) - d(S) \geq -d(S) \geq -d_j
    \end{align*}
    Observe that $L_{max} = C_j - d_j$. Hence in this schedule, it holds 
    \begin{align*}
        L_{max} = C_j - d_j \leq 2L_{max}^*
    \end{align*}
    which justifies the 2-approximation ratio.
\end{proof}

\section{Scheduling on Identical Parallel Machines}
Just as we can run $k$-bands of Turing machines in parallel, jobs can be processed simultaneously on 
$k$ machines, if available. The problem setting is then a bit different: there is no release date of jobs, and 
the optimization goal is to minimize the time all jobs are finished. 
\begin{definition}[Job Scheduling on Identical Parallel Machines]
    Given $n$ jobs to be processed on $k$ identical parallel machines, each job $j$ has a processing time $p_j$ with $j = 1, \cdots, n$.
    Suppose job $j$ is finished at time $C_j$, the minimization goal, the makespan, is defined as
    \begin{align*}
        C_{max} = \max_{j = 1, \cdots, n} C_j
    \end{align*}
\end{definition}
For this problem, we present a local search algorithm and a greedy algorithm. The ideas of both algorithms 
are both simple, while the analysis requires some effort.

\subsection{Local Search Algorithm}
The local search algorithm starts with an arbitrary schedule. In each step, we try to find a better schedule for the last job to be completed. 
More specifically, we traverse all machines, and try to move the job to another machine such that it finishes earlier. 
Whenever no such move is possible, the algorithm terminates. To simply the analysis, we assume that there is no idle time on any machine in the initial schedule.  
Again, we start with a lowerbound on the size of the optimal solution. 
\begin{lemma}
    \label{lemma:lowerbound2}
    For a scheduling problem with $n$ jobs and $k$ identical machines, its optimal makespan is less equal than the average processing time of all jobs.
    \begin{align*}
        C_{max}^* \geq \frac{1}{k} \sum_{j=1, \cdots, n} p_j
    \end{align*} 
\end{lemma}
\begin{proof}
    We perform a case distinction.\\
        \textbf{Case 1:} All machines terminate at the same time. In this case, each machine runs exactly the average processing time, i.e. the equality holds in the lemma. \\
        \textbf{Case 2:} At least two machines do not finish at the same time. In this case, the machine that finishes later runs more than the average processing time. Furthermore, the optimal solution has to run no shorter than this machine. \\
        Hence the strict inequality holds in the lemma.
\end{proof}
Using the same idea, we observe that the starting time of the last job satisfies an upperbound. 
\begin{observation}
    \label{observation:upperbound}
    Let $j$ be the last job completed in the local search algorithm. We denote its starting time as $S_j = C_j - p_j$. It holds 
    \begin{align*}
        S_j \leq \frac{1}{k} \sum_{j=1, \cdots, n} p_j
    \end{align*}
\end{observation}
\begin{proof}
    If the last job is completed just as the average processing time, its starting time has to be strictly less than the average processing time. 
    Otherwise, we suppose for contradiction that $S_j > \frac{1}{k} \sum_{j=1, \cdots, n} p_j$. By the strategy of the local search algorithm,
    all other machines are still running at time $S_j$, otherwise the job can be moved to another machine. Hence all machines terminate 
    later than $S_j$, implying that all machines terminate later than the average processing time. Since not all machines can terminate later than 
    the average processing time, this is a contradiction. 
\end{proof}
Combining the two observations, we obtain $C_{max}^* > S_j$. Observe that $p_j \leq C_j$ by definition. 
Hence we obtain the approximation ratio for this local search algorithm.
\begin{theorem}
    \label{theorem:localsearch}
    The local search algorithm yields a $2$-approximation ratio.
\end{theorem}
\begin{proof}
    Let $j$ be the last job completed. We have
    \begin{align*}
        C_{max} = C_j = S_j + p_j \leq C_{maxc}^* + p_j \leq 2C_{max}^*
    \end{align*}
\end{proof}
While it is easy to find a approximation ratio, the polynomial time complexity of the local search algorithm 
is not trivial. Observe that the algorithm terminates only if no job can be moved to improve the schedule. 
\color{red} omit the analysis(and refinement) here? cuz not enough space \color{black}

\subsection{Greedy Algorithm}
The greedy algorithm is similar to the \textbf{EDD} rule in the previous section. Whenever a machine is available, 
we assign it a job from the job list. Since there is no release date, the choice is arbitrary. 
This is referred to as \textbf{list scheduling} algorithm. The execution of the list scheduling algorithm can 
be viewed as a special case of the \textbf{local search} algorithm, where the initial schedule cannot be improved.
\begin{theorem}
    The \textbf{list scheduling} algorithm yields a $2$-approximation ratio.
\end{theorem}
\begin{proof}
    Let $j$ be the last job completed in a schedule outputed by the \textbf{list scheduling} algorithm. 
    Suppose the \textbf{local search} algorithm can improve the schedule. 
    Then we can find a machine such that $S_j' < S_j$ where $S_j'$ is the new starting time of $j$ after moving it to 
    this new machine. However, the greedy strategy always assigns the job to the first available machine, hence 
    no such machine exists. Thus, the schedule cannot be improved by \textbf{local search} algorithm. 
    Hence its approximation ratio can also bounded by $\alpha = 2$ as in theorem \cref{theorem:localsearch}.
\end{proof}
If we execute the \textbf{list scheduling} algorithms on some examples \color{red} fill in graphs if needed \color{black}, we can observe that the longer the processing time of the last job, 
the worse the approximation ratio is. If we process the longer jobs first, and fill in the shorter jobs later,
the approximation ratio may be improved. This is the idea of the longest processing time rule(\textbf{LPT}).
As expected it yields a better approximation ratio. 
\begin{theorem}
    The \textbf{LPT}-rule algorithm yields a $4/3$-approximation ratio.
\end{theorem}
\begin{proof}
    Recall in lemma \cref{lemma:lowerbound2}, we have proven that the optimal makespan is bounded by the average processing time.
    Let $E =  \sum_{j=1, \cdots, n} p_j$ as the average processing time.
    Suppose for contradiction that $C_{max} > \frac{4}{3} C_{max}^*$ for the last completed job $j$. 
    When $j$ started, its starting time $C_j - p_j$ must be less equal 
    than $E$. If not, there must have been another machine finishing at time $E$ or earlier, to which we could have moved job $j$
    for a better schedule. Hence we have 
    \begin{align*}
        p_j \geq C_j - E = C_{max} - E > \frac{4}{3}C_{max}^* - C_{max}^* = \frac{1}{3} C_{max}^*
    \end{align*}
    In \textbf{LPT}-rule, we can assume the last job completed always has the shortest processing time.
    If it is not the case, we simply discard the shorter jobs, while the new job list still has the same makespan. 
    Thus, for each job $i = 1, \cdots, n$, it holds $p_i \geq p_j > \frac{1}{3}C_{max}^*$. 
    There are hence at most two jobs on each machine, otherwise the optimal makespan would exceed $C_{max}^*$. 
    We are able to show that \textbf{LPT}-rule yields the optimal solution by case distinction.

    \textbf{Case 1:} There is no job processed before $j$ on the same machine. Since $j$ is the shortest job, 
    we conclude that each machine processes at most one job, and the optimal solution is obtained.\\
    \textbf{Case 2:} There is a job processed before $j$ on the same machine. Since there are at most two jobs on each 
    machine, we may assume that there are $k + k'$ jobs in total, where $k' \leq k$. 
    Sort the jobs reversely with regard to their processing time. The optimal schedule is assigning $(k + i)$-th job 
    directly after the $i$-th job, where $i < k'$. If $(k+k')$-th job is assigned after a job finishing later than $k'$-th job, it will 
    definitely finishes later than the optimal schedule. If it is assigned after a job finishing earlier than $k'$-th job, 
    a job that takes longer will be assigned after the $k'$-th job, which is also suboptimal.\\
    To summarize, the optimal schedule is obtained by the \textbf{LPT}-rule algorithm, which contradicts with the assumption $C_{max} > \dfrac{4}{3} C_{max}^*$.
\end{proof}

@@

Many graph problems are known to be \NP-hard. Furthermore, greedy algorithms are known to be useful in computing 
many graph structures in polynomial-time such as minimum spanning trees, shortest paths etc. Unaccidentally, 
this strategy is also useful in term of approximation algorithms. 

@@

    Find $k$ centers $S \subseteq P$ s.t. the maximal distance from any point to its nearest center is minimized.

@@

The problem can be reduced to a problem in undirected weighted graph, where the weight is the distance between two vertices. 

@@

is farthest from the current centers, i.e. choosing $\arg \max d(p, S)$ from $p \in P \backslash S$. 
By adding such point to the center set in $(k-1)$ iterations, we obtain an approximation for $k$-Center .

@@

    The presented greedy problem yields a $2$-approximation ratio for $k$-Center .

@@

    A more interesting case is when not all clusters have a point selected as center. 
    There would be then at least two points, $p$ and $q$,  from the same cluster. By the presented upperbound, 

@@

we reduce $k$-Center from Dominating Set, which is an \NP-hard decision problem.

@@

    If there is polynomial-time approximation algorithm for $k$-Center  with $\alpha < 2$, 

@@

    Hence the approximation yields the optimal solution for $k$-Center , which results 

>>>>

\title{Approximation Algorithms: Greedy Algorithm and Local Search}
\author{Zixuan Fan\thanks{Department of Computer Science, Technical University of Munich. {\tt ge43yeb@mytum.de}}}
\maketitle
\section{Introduction}
The theory of computer science has grown significantly throughout the past century. Among many topics, \NP-hardness has drawn the attention of many researchers. 
While there is no proof whether $\PTIME=\NP$, people tend to be interested in compensation: solving NP-hard problems with a sub-optimal solution in polynomial time, which is the motivation of approximation algorithms. This paper introduces two fundamental techniques in designing approximation algorithms: greedy algorithm and local search.
We start with some mathematical backgrounds, followed by a brief introduction of greedy and local search. 
Then, we present a few examples that exploit these techniques.

@@

\subsection{Greedy Algorithms and Local Search}
Both greedy algorithms and local search construct the solution step by step. 
In each step, the strategy makes certain decisions to optimize the result locally. 
The difference between the two techniques lies in the strategy of making decisions. 
The greedy algorithms try to make the best decision at each step, and the solution is not guaranteed to 
be \textit{feasible} at the beginning. On the other hand, local search starts with an arbitrary feasible solution
and maintains the feasibility while improving the solution. 
Hence, greedy algorithms are called \textit{primal infeasible} algorithms, while local search algorithms 
are referred to as \textit{primal feasible} algorithms.

\section{Scheduling on A Single Machine}
Scheduling, or Job Sequencing, is one of the earliest discovered NP-complete problems. 
It was amongst the first 21 NP-complete problems published by Karp in 1972. In this section, 
we examine a simplified version of the problem: only one machine is available for scheduling.
\begin{definition}[Scheduling on Single Machine]
    Given $n$ jobs to be processed with processing time $p_j$, release time $r_j \geq 0$, and deadline $d_j$ with $j = 1, \cdots, n$.
    Suppose $j$-th job is completed at time $C_j$. We define the lateness as $L_j = C_j - d_j$. The goal is to minimize the maximal lateness 
    \begin{align*}
        L_{max} = \max_{j = 1, \cdots, n} L_j
    \end{align*}
\end{definition} 
Unfortunately, the problem is \NP-hard, and it remains \NP-hard even if we apply 
a few constraints to it. \textbf{cite the source} One exceptional case is when all deadlines are non-negative: the lateness is always positive. 
We are able to give a 2-approximation algorithm for this case. The algorithm simply exploits the earliest due date rule(\textbf{EDD}). 
Just as the name suggests, whenever the machine finishes a job, it picks the job with the earliest due date from all \textbf{available} jobs.
Here, a job is \textit{available} at time $t$ if $r_j \leq t$.

To analyze the algorithm, we have to introduce a few notations. Let $S$ denote a set of jobs, $r(S) = \min_{j \in S} r_j$, $p(S) = \sum_{j \in S} p_j$, 
and $d(S) = \max_{j \in S} d_j$. While $L_{max}$ denotes the maximal lateness computed by the algorithm, $L_{max}^*$ denotes the optimal solution. 
As preparation, an interesting lower bound on the optimal solution is observed. 
\begin{lemma}
    \label{lemma:lowerbound}
    For any set of jobs $S$, $L_{max}^* \geq r(S) + p(S) - d(S)$
\end{lemma}
\begin{proof}
    Suppose job $j$ is the last finished job in the optimal schedule. The scheduling cannot start until $r(S)$. In an optimal schedule, there is no gap between the processing of jobs, and all jobs 
    are processed consecutively in $p(S)$. Hence, $j$ cannot be finished until $r(S) + p(S)$. In addition, we have $d_j \leq d(S)$ by definition. It follows 
    \begin{align*}
        L_{max}^* \geq L_j = C_j - d_j \geq r(S) + p(S) - d_j \geq r(S) + p(S) - d(S)
    \end{align*} 
\end{proof}
We then take a closer look at the \textbf{EDD} rule. Suppose the release time $r_j$, processing time $p_j$, and the deadline $d_j$ are encoded as a ternary tuple $(r_j, p_j, d_j)$.
The only part that requires heavy computation for \textbf{EDD} rule is choosing the job with the earliest due date.
The easiest implementation is to preserve a linked list to store the information of each job, which takes $\bigo{n^2}$ time in total. 
A more efficient implementation takes advantage of a FIFO queue, which takes only $\bigo{n}$ time. In either case, 
the algorithm runs in polynomial time. This directly leads to the following theorem.
\begin{theorem}
    The EDD-rule algorithm runs in polynomial time. 
\end{theorem}
What we care more about in the context of approximation algorithms is the approximation ratio. We then show that the algorithm yields the promised approximation ratio.
\begin{theorem}
    The EDD-rule algorithm yields a 2-approximation ratio.
\end{theorem}
\begin{proof}
    Suppose $j$ is the job with the maximal lateness in the schedule generated by the \textbf{EDD} rule.
    Let $t$ be the earliest time for the machine to keep processing jobs continuously in the interval $[t, C_j]$.
    Let $S$ be the set of jobs that are processed in this interval. In our assumption, $r(S) = t$ is guaranteed. 
    Suppose for contradiction that $r(S) > t$, the processing would not be able to start at time $t$. 
    Similarly, if $r(S) < t$, the processing would start earlier than $t$. Both cases contradict the assumption.
    Furthermore, $p(S) = C_j - t$, for the processing is continuous, and it stops at time $C_j$. Applying lemma \cref{lemma:lowerbound},
    we obtain 
    \begin{align*}
        L_{max}^* \geq r(S) + p(S) - d(S) = t + C_j - t - d(S) = C_j - d(S) \geq C_j
    \end{align*}
    Additionally, it holds $d_j < d(S)$ by definition. Applying the same lemma, we have
    \begin{align*}
        L_{max}^* \geq r(S) + p(S) - d(S) \geq -d(S) \geq -d_j
    \end{align*}
    Observe that $L_{max} = C_j - d_j$. Hence, it holds for this schedule
    \begin{align*}
        L_{max} = C_j - d_j \leq 2L_{max}^*
    \end{align*}
    which justifies the 2-approximation ratio.
\end{proof}

\section{Scheduling on Identical Parallel Machines}
Just as we can run $k$-bands of Turing machines in parallel, jobs can be processed simultaneously on 
$k$ machines, if available. The problem setting is then different: there is no release date for jobs, and 
the optimization goal is to minimize the time all jobs are finished. 
\begin{definition}[Job Scheduling on Identical Parallel Machines]
    Given $n$ jobs to be processed on $k$ identical parallel machines, each job $j$ has a processing time $p_j$ with $j = 1, \cdots, n$.
    Suppose job $j$ is finished at time $C_j$, the minimization goal, the makespan, is defined as
    \begin{align*}
        C_{max} = \max_{j = 1, \cdots, n} C_j
    \end{align*}
\end{definition}
For this problem, we present a local search algorithm and a greedy algorithm. The ideas of both algorithms 
are both simple, while the analysis requires some effort.

\subsection{Local Search Algorithm}
The local search algorithm starts with an arbitrary schedule. In each step, we try to find a better schedule for the last job to be completed. 
More specifically, we traverse all machines and try to move the job to another machine so that it finishes earlier. 
Whenever no such move is possible, the algorithm terminates. To simplify the analysis, we assume that there is no idle time on any machine in the initial schedule.  
Again, we start with a lower bound on the size of the optimal solution. 
\begin{lemma}
    \label{lemma:lowerbound2}
    For a scheduling problem with $n$ jobs and $k$ identical machines, its optimal makespan is less than or equal to the average processing time of all jobs.
    \begin{align*}
        C_{max}^* \geq \frac{1}{k} \sum_{j=1, \cdots, n} p_j
    \end{align*} 
\end{lemma}
\begin{proof}
    We perform a case distinction.\\
        \textbf{Case 1:} All machines terminate at the same time. In this case, each machine runs exactly the average processing time, i.e., the equality holds in the lemma. \\
        \textbf{Case 2:} At least two machines do not finish at the same time. In this case, the machine that finishes later runs more than the average processing time. Furthermore, the optimal solution has to run no shorter than this machine. \\
        Hence, strict inequality is held in the lemma.
\end{proof}
Using the same idea, we observe that the starting time of the last job satisfies an upper bound. 
\begin{observation}
    \label{observation:upperbound}
    Let $j$ be the last job completed in the local search algorithm. We denote its starting time as $S_j = C_j - p_j$. It holds 
    \begin{align*}
        S_j \leq \frac{1}{k} \sum_{j=1, \cdots, n} p_j
    \end{align*}
\end{observation}
\begin{proof}
   If the last job is completed as soon as the average processing time, its starting time has to be strictly less than the average processing time. 
    Otherwise, we suppose for contradiction that $S_j > \frac{1}{k} \sum_{j=1, \cdots, n} p_j$. By the strategy of the local search algorithm,
    all other machines are still running at time $S_j$. Otherwise, the job can be moved to another machine. Hence, all machines terminate 
    later than $S_j$, implying that all machines terminate later than the average processing time. Since not all machines can terminate later than 
    the average processing time, this is a contradiction. 
\end{proof}
Combining the two observations, we obtain $C_{max}^* > S_j$. Observe that $p_j \leq C_j$ by definition. 
Hence, we obtain the approximation ratio for this local search algorithm.
\begin{theorem}
    \label{theorem:localsearch}
    The local search algorithm yields a $2$-approximation ratio.
\end{theorem}
\begin{proof}
    Let $j$ be the last job completed. We have
    \begin{align*}
        C_{max} = C_j = S_j + p_j \leq C_{maxc}^* + p_j \leq 2C_{max}^*
    \end{align*}
\end{proof}
While it is easy to find an approximation ratio, the polynomial time complexity of the local search algorithm 
is not trivial. Observe that the algorithm terminates only when no job can be moved to improve the schedule. 
\color{red} omit the analysis(and refinement) here? cuz not enough space \color{black}

\subsection{Greedy Algorithm}
The greedy algorithm is similar to the \textbf{EDD} rule in the previous section. Whenever a machine is available, 
we assign it a job from the job list. Since there is no release date, the choice is arbitrary. 
This is referred to as \textbf{list scheduling} algorithm. The execution of the list scheduling algorithm can 
be viewed as a special case of the \textbf{local search} algorithm, where the initial schedule cannot be improved.
\begin{theorem}
    The \textbf{list scheduling} algorithm yields a $2$-approximation ratio.
\end{theorem}
\begin{proof}
    Let $j$ be the last job completed in a schedule output by the \textbf{list scheduling} algorithm. 
    Suppose the \textbf{local search} algorithm can improve the schedule. 
    Then, we can find a machine such that $S_j' < S_j$ where $S_j'$ is the new starting time of $j$ after moving it to 
    this new machine. However, the greedy strategy always assigns the job to the first available machine, so 
    no such machine exists. Thus, the schedule cannot be improved by \textbf{local search} algorithm. 
    Hence, its approximation ratio can also bounded by $\alpha = 2$ as in theorem \cref{theorem:localsearch}.
\end{proof}
If we execute the \textbf{list scheduling} algorithms on some examples \color{red} fill in graphs if needed \color{black}, we can observe that the longer the processing time of the last job, 
the worse the approximation ratio is. If we process the longer jobs first and fill in the shorter jobs later,
the approximation ratio may be improved. This is the idea of the longest processing time rule(\textbf{LPT}).
As expected, it yields a better approximation ratio. 
\begin{theorem}
    The \textbf{LPT}-rule algorithm yields a $4/3$-approximation ratio.
\end{theorem}
\begin{proof}
    Recall in lemma \cref{lemma:lowerbound2}, we have proven that the optimal makespan is bounded by the average processing time.
    Let $E =  \sum_{j=1, \cdots, n} p_j$ as the average processing time.
    Suppose for contradiction that $C_{max} > \frac{4}{3} C_{max}^*$ for the last completed job $j$. 
    When $j$ started, its starting time $C_j - p_j$ must be less than or equal to
 $E$. If not, there must have been another machine finishing at time $E$ or earlier, to which we could have moved job $j$
    for a better schedule. Hence we have 
    \begin{align*}
        p_j \geq C_j - E = C_{max} - E > \frac{4}{3}C_{max}^* - C_{max}^* = \frac{1}{3} C_{max}^*
    \end{align*}
    In \textbf{LPT}-rule, we can assume the last job completed always has the shortest processing time.
    If this is not the case, we simply discard the shorter jobs while the new job list still has the same makespan. 
    Thus, for each job $i = 1, \cdots, n$, it holds $p_i \geq p_j > \frac{1}{3}C_{max}^*$. 
    There are, thus, at most two jobs on each machine. Otherwise, the optimal makespan would exceed $C_{max}^*$. 
    We are able to show that \textbf{LPT}-rule yields the optimal solution by case distinction.

    \textbf{Case 1:} There is no job processed before $j$ on the same machine. Since $j$ is the shortest job, 
    we conclude that each machine processes at most one job, and the optimal solution is obtained.\\
    \textbf{Case 2:} There is a job processed before $j$ on the same machine. Since there are at most two jobs on each 
    machine, we may assume that there are $k + k'$ jobs in total, where $k' \leq k$. 
    Sort the jobs reversely with regard to their processing time. The optimal schedule is assigning $(k + i)$-th job 
    directly after the $i$-th job, where $i < k'$. If $(k+k')$-th job is assigned after a job finishes later than the $k'$-th job, it will 
    definitely finish later than the optimal schedule. If it is assigned after a job finishing earlier than the $k'$-th job, 
    a job that takes longer will be assigned after the $k'$-th job, which is also suboptimal.\\
    To summarize, the optimal schedule is obtained by the \textbf{LPT}-rule algorithm, which contradicts the assumption $C_{max} > \dfrac{4}{3} C_{max}^*$.
\end{proof}

@@

Many graph problems are known to be \NP-hard. Furthermore, greedy algorithms are known to be helpful in computing 
many graph structures in polynomial time, such as minimum spanning trees, shortest paths, etc. Unaccidentally, 
this strategy is also helpful in terms of approximation algorithms. 

@@

    Find $k$ centers $S \subseteq P$ so that the maximal distance from any point to its nearest center is minimized.

@@

The problem can be reduced to a problem in an undirected weighted graph, where the weight is the distance between two vertices. 

@@

is farthest from the current centers, i.e., choosing $\arg \max d(p, S)$ from $p \in P \backslash S$. 
By adding such a point to the center set in $(k-1)$ iterations, we obtain an approximation for $k$-Center.

@@

    The presented greedy problem yields a $2$-approximation ratio for $k$-Center.

@@

    A more interesting case is when not all clusters have a point selected as a center. 
    There would be then at least two points, $p$ and $q$,  from the same cluster. By the presented upper bound, 

@@

we reduce $k$-Center from Dominating Set, an \NP-hard decision problem.

@@

    If there is a polynomial-time approximation algorithm for $k$-Center  with $\alpha < 2$, 

@@

    Hence, the approximation yields the optimal solution for $k$-Center, which results 
